Confirmation of \srcfull{} as a long period radio transient

### 2025-04-26 paper/main.tex
Updated paper with timing ephemeris table

Because the large scattering time scale at low frequencies significantly distorts the pulse shapes, we identified the times of arrival (ToAs) with the fitted $\mu$ parameter in the fits given in Eq. \eqref{eqn:emg}, which represents the location of the Gaussian pulse before scattering.

The distortion of the pulse shapes at MWA frequencies creates a degeneracy between DM and scattering time scales that is not easily disambiguated.
This is demonstrated in Fig. \ref{fig:stacked_spectra}, which shows stacked MWA and MeerKAT spectra.
Without accounting for scattering, the measured DM would significantly exceed the 710\,pc\,cm$^{-3}$ (cyan lines).
The scattering predicted by Galactic electron density models, however, is sufficient to account for the apparent extra delay.

@@

The degeneracy between DM and scattering (as well as variations in pulse width and ToA) render the lower frequency pulses less useful for measuring either DM or scattering alone.
Breaking the degeneracy is possible in principle with a much higher S/N average profile than what is possible with the current data set.

For this work, we therefore did not attempt to fit the DM or the scattering time scale individually.
Instead, we adopted the original ASKAP measurement of ${\rm DM} = 710\,$pc\,cm$^{-3}$ and a scattering timescale of $\tau_{\rm sc,1 GHz} = 0.07\,$s for the timing analysis.
We did, however, confirm that fits to individual pulses using Eq. \eqref{eqn:emg}, but also allowing the $\tau$ parameter to freely vary, produced fitted values that were broadly consistent with our chosen value.

The ToAs were then fit

>>>>

Because the large scattering time scale at low frequencies significantly distorts the pulse shapes, we identified the times of arrival (ToAs) with the fitted $\mu$ parameter in the fits given in Eq. \eqref{eqn:emg}, which represents the location of the assumed Gaussian pulse before scattering.

The distortion of the pulse shapes at MWA frequencies creates a degeneracy between DM and scattering time scales that is not easily disambiguated.
This is demonstrated in Fig. \ref{fig:stacked_spectra}, which shows stacked MWA and MeerKAT spectra.
Without accounting for scattering, the measured DM would significantly exceed the 771\,pc\,cm$^{-3}$ (cyan lines).
The scattering predicted by Galactic electron density models, however, is sufficient to account for the apparent extra delay.

@@

The degeneracy between DM and scattering (as well as variations in pulse width and ToA) render the lower frequency pulses less useful for measuring either DM or scattering alone (\todo{see Appendix \dots}).
Breaking the degeneracy is possible in principle with a much higher S/N average profile than what is possible with the current data set.
Having said that, we note that fits of Eq. \eqref{eqn:emg} to the brightest MWA pulses where the scattering time scale was left as a free parameter were broadly consistent with the predictions of the NE2001 and YMW16 models.

Because the scattering time scale could not be reliably measured for all individual pulses, we obtained ToAs by assuming a fixed scattering time of $\tau_{\rm sc,1 GHz} = 0.07\,$s.
These ToAs were then barycentred and fit for both period and DM, resulting in the values given in Table \ref{tbl:ephemeris}.
We also tried fitting a timing model that included a spin-down parameter, and found that it was consistent with zero spin-down to within $1\sigma$.

\begin{table}
  \caption{Timing ephemeris for \src{}}
  \label{tbl:ephemeris}
  \begin{tabular}[lc]
    \hline
    Parameter & Value \\
    \hline
    Period (s) & $4186.3288 \pm 0.0003$ \\
    PEPOCH (MJD) & $59965.03783 \pm 0.00003$ \\
    DM (pc/cm$^{-3}$) & $771 \pm 27$ \\
    \hline
  \end{tabular}
\end{table}
